R Notebook

### 2021-07-28 Old scripts/pupil_arousal_datarmd.Rmd
one more

timecourse_result_df%>%
  ggplot(aes(timebins, t))+
  geom_line(size = 2)+
  geom_line(aes(y = p), linetype = "dashed", size = 2)+
  geom_hline(yintercept = .05, color = 'red', size = 1.5)

@@

@@

timecourse_result_df_val_and_ar%>%
  ggplot(aes(timebins, t))+
  geom_line(size = 2)+
  geom_line(aes(y = p), linetype = "dashed", size = 2)+
  geom_hline(yintercept = .05, color = 'red', size = 1.5)

@@

timecourse_result_df_val_and_ar_low%>%
  ggplot(aes(timebins, t))+
  geom_line(size = 2)+
  geom_line(aes(y = p), linetype = "dashed", size = 2)+
  geom_hline(yintercept = .05, color = 'red', size = 1.5)

@@

pupil_arousal_findings$arousal_scr <- lmer(BIO_CDA.PhasicMax_z ~ valence_c +(1+arousal_c|ssid),
                        REML = FALSE,
                        data = subset(db_full4new_stim_screen_pupil_nopract_nt,
                                      pp_arousal_outler == FALSE))
                                      # mediansplit_self_valence == "More positive"))

@@

scr_models$scr2<- lmer(BIO_CDA.ISCR_collapsed ~  arousal_c*valence_c *TASc+
                                           (1| ssid) +
                                           (1 | stimIAPS),
                        REML = FALSE,
                        data =  subset(db_full4new_stim_screen_pupil_nopract_nt, scr_utl == "notoutlier"))

@@

scr_models$scr2<- lmer(BIO_CDA.SCR_collapsed ~  arousal_c* valence_c *TASc+
                                           (1| ssid) +
                                           (1 | stimIAPS),
                        REML = FALSE,
                        data =  subset(db_full4new_stim_screen_pupil_nopract, Group = "NT"))

@@

heart rate

@@

```{r}
# test - analyse just positive
hr_dif_models$arousal_val <- lmer(Bio_Mean_HR_dif ~  valence_c *arousal_c+
                                        + (1 | ssid) + (1|stimIAPS),
                                        # (1|mediansplit_sample_arousal2),
     REML = FALSE,
     data = subset(db_full6new_hr_fix_stim_nt1, mediansplit_ground_valence == "More positive" & Bio_Mean_HR_dif_outl == "not outlier"  & Group == "NT"))

@@

unique(db_full6new_hr_fix_stim_nt1$ssid)
hr_dif_models$valfrom_hr <- lmer(valence_c ~   Bio_Mean_HR_dif* arousal_c+
                                        + (1 | ssid) + (1|stimIAPS),
                                        # (1|mediansplit_sample_arousal2),
     REML = FALSE,
     data = subset(db_full6new_hr_fix_stim_nt1, mediansplit_ground_valence == "More positive" &
                   Bio_Mean_HR_dif_outl == "not outlier" & Group == "NT"))
arousal_c

summary(hr_dif_models$valfrom_hr)

@@

@@

db_full6new_hr_fix_stim_nt1%>%
  subset(Condition == "IAPS")%>%
  group_by(stimIAPS, mediansplit_ground_valence)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(mediansplit_ground_valence, arousal))+
  stat_summary(geom = 'pointrange')+
  ggpubr::stat_compare_means()+
  geom_text(aes(label = stimIAPS))

@@

# try and regress valence our oarousal_val

@@

>>>>

timecourse_result_df%>%
  ggplot(aes(timebins, Estimate))+
  geom_line(size = 2)+
  geom_line(aes(y = p), linetype = "dashed", size = 2)+
  geom_hline(yintercept = .05, color = 'red', size = 1.5)

@@

subset(tmp.df4_full_stim_downs_jun2021_with_behnew,
                                    mediansplit_ground_valence == "More negative" & 
                                    timebin_no == nbins[b])%>%
  ggplot(aes(ArousalMean))

@@

timecourse_result_df_val_and_ar%>%
  ggplot(aes(timebins, Estimate))+
  geom_line(size = 2)+
  geom_line(aes(y = p), linetype = "dashed", size = 2)+
  geom_hline(yintercept = .05, color = 'red', size = 1.5)

@@

timecourse_result_df_val_and_ar_low%>%
  ggplot(aes(timebins, Estimate))+
  geom_line(size = 2)+
  geom_line(aes(y = p), linetype = "dashed", size = 2)+
  geom_hline(yintercept = .05, color = 'red', size = 1.5)

@@

pupil_arousal_findings$arousal_scr <- lmer(BIO_CDA.PhasicMax_z ~ valence_c +(1|ssid),
                        REML = FALSE,
                        data = subset(db_full4new_stim_screen_pupil_nopract_nt,
                                      pp_arousal_outler == FALSE))
                                      # mediansplit_self_valence == "More positive"))

@@

scr_models$scr2<- lmer(BIO_CDA.ISCR_collapsed ~  arousal_c*valence_c+
                                           (1| ssid) +
                                           (1 | stimIAPS),
                        REML = FALSE,
                        data =  subset(db_full4new_stim_screen_pupil_nopract_nt, scr_utl == "notoutlier"))

@@

scr_models$scr2<- lmer(BIO_CDA.SCR_collapsed ~  arousal_c* valence_c +
                                           (1| ssid) +
                                           (1 | stimIAPS),
                        REML = FALSE,
                        data =  subset(db_full4new_stim_screen_pupil_nopract, Group = "NT"))

@@

heart rate
```{r}

@@

```{r}
unique(db_full6new_hr_fix_stim_nt1$Group)
# test - analyse just positive
hr_dif_models$arousal_val <- lmer(Bio_Mean_HR_dif ~   valence_c+
                                        + (1 | ssid) + 
                                    (1|stimIAPS),
                                        # (1|mediansplit_sample_arousal2),
     REML = FALSE,
     data = subset(db_full6new_hr_fix_stim_nt1, 
                   # mediansplit_ground_valence == "More negative" &
                     Bio_Mean_HR_dif_outl == "not outlier"  & Group == "NT"))

hr_dif_models$arousal_AR <- lmer(Bio_Mean_HR_dif ~   arousal_c+
                                        + (1 | ssid) + 
                                    (1|stimIAPS),
                                        # (1|mediansplit_sample_arousal2),
     REML = FALSE,
     data = subset(db_full6new_hr_fix_stim_nt1, 
                   # mediansplit_ground_valence == "More negative" &
                     Bio_Mean_HR_dif_outl == "not outlier"  & Group == "NT"))

summary(hr_dif_models$arousal_AR)

unique(db_full6new_hr_fix_stim_nt1$ssid)
hr_dif_models$valfrom_hr <- lmer(arousal_c ~   Bio_Mean_HR_dif* valence_c+
                                        + (1 | ssid) + (1|stimIAPS),
                                        # (1|mediansplit_sample_arousal2),
     REML = FALSE,
     data = subset(db_full6new_hr_fix_stim_nt1, 
                   # mediansplit_ground_valence == "More positive" &
                   Bio_Mean_HR_dif_outl == "not outlier" & Group == "NT"))
arousal_c
summary(hr_dif_models$valfrom_hr)

install.packages("glmmLasso")
require(glmmLasso)
?glmmLasso::glmmLasso()

HR_dif_forlasso<- subset(db_full6new_hr_fix_stim_nt1, 
                   # mediansplit_ground_valence == "More positive" &
                   Bio_Mean_HR_dif_outl == "not outlier" & Group == "NT")

HR_dif_forlasso<- HR_dif_forlasso%>%subset(!is.na(valence_c))

HR_dif_forlasso$ssid<- as.factor(HR_dif_forlasso$ssid)
lassomodels<- list()

lassomodels$firt<- glmmLasso(Bio_Mean_HR_dif ~ arousal_c + valence_c, rnd = list(ssid=~1), 
       lambda=1000, data = HR_dif_forlasso, final.re=TRUE)

# table(is.na(HR_dif_forlasso$arousal_c))
# 
# table(is.na(HR_dif_forlasso$valence_c))

summary(lassomodels$firt)

################# More Elegant Method ############################################
## Idea: start with big lambda and use the estimates of the previous fit (BUT: before
## the final re-estimation Fisher scoring is performed!) as starting values for the next fit;
## make sure, that your lambda sequence starts at a value big enough such that all covariates are
## shrinked to zero;

## Using BIC (or AIC, respectively) to determine the optimal tuning parameter lambda
lambda <- seq(500,0,by=-5)

BIC_vec<-rep(Inf,length(lambda))
# family = poisson(link = log)

# specify starting values for the very first fit; pay attention that Delta.start has suitable length! 
Delta.start<-as.matrix(t(rep(02)))
Q.start<-0.1  
HR_dif_forlasso_1<- select(HR_dif_forlasso, c(ssid, valence_c, arousal_c,Bio_Mean_HR_dif))
table(is.na(HR_dif_forlasso$Bio_Mean_HR_dif))
J = 1

for (j in lambda) {

  glm3 <- glmmLasso(Bio_Mean_HR_dif ~ arousal_c + valence_c, rnd = list(ssid=~1),  
                    # family = family,
                    data = HR_dif_forlasso_1, 
                    lambda=500, 
                    switch.NR=F,
                    final.re=TRUE,
                    control = list(start=Delta.start[j],
                                   q_start=Q.start[j]))

  # print(colnames(glm3$Deltamatrix)[2:7][glm3$Deltamatrix[glm3$conv.step,2:7]!=0])
  # BIC_vec[j]<-glm3$bic
  # Delta.start<-rbind(Delta.start,glm3$Deltamatrix[glm3$conv.step,])
  # Q.start<-c(Q.start,glm3$Q_long[[glm3$conv.step+1]])
  }

opt3<-which.min(BIC_vec)

glm3_final <- glmmLasso(points~transfer.spendings + ave.unfair.score 
                        + ball.possession
                        + tackles + ave.attend + sold.out, rnd = list(team=~1),  
                        family = family, data = soccer, lambda=lambda[opt3],
                        switch.NR=F,final.re=TRUE,
                        control = list(start=Delta.start[opt3,],q_start=Q.start[opt3]))

summary(glm3_final)

## plot coefficient paths
par(mar=c(6,6,4,4))
plot(lambda,Delta.start[2:(length(lambda)+1),2],type="l",ylim=c(-1e-1,1e-1),ylab=expression(hat(beta[j])))
lines(c(-1000,1000),c(0,0),lty=2)
for(i in 3:7){
  lines(lambda[1:length(lambda)],Delta.start[2:(length(lambda)+1),i])
}
abline(v=lambda[opt3],lty=2)
```

hr_dif_models$arousal_val <- lmer(Bio_Mean_HR_dif ~   valence_c* arousal_c+
                                        + (1 | ssid),
                                    # (1|stimIAPS),
                                        # (1|mediansplit_sample_arousal2),
     REML = FALSE,
     data = subset(db_full6new_hr_fix_stim_nt1, 
                   # mediansplit_ground_valence == "More negative" &
                     # Bio_Mean_HR_dif_outl == "not outlier"  & 
                     Group == "NT"))

@@

car::vif(hr_dif_models$arousal_val)

@@

interactions::interact_plot(hr_dif_models$arousal_val, pred =arousal_c , modx =  valence_c)

@@

db_full6new_hr_fix_stim_nt1$groung%>%
  subset(Condition == "IAPS")%>%
  group_by(stimIAPS, mediansplit_ground_valence)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(mediansplit_ground_valence, arousal))+
  stat_summary(geom = 'pointrange')+
  ggpubr::stat_compare_means()+
  geom_text(aes(label = stimIAPS))

@@

# try and regress valence our oarousal_val
```{r}

@@

```{r}
summary(hr_dif_models$arousal_val_cat)
